---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# paletteer

<!---
[![Travis build status](https://travis-ci.org/EmilHvitfeldt/paletteer.svg?branch=master)](https://travis-ci.org/EmilHvitfeldt/paletteer)
[![Coverage status](https://codecov.io/gh/EmilHvitfeldt/paletteer/branch/master/graph/badge.svg)](https://codecov.io/github/EmilHvitfeldt/paletteer?branch=master)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/EmilHvitfeldt/paletteer?branch=master&svg=true)](https://ci.appveyor.com/project/EmilHvitfeldt/paletteer)
[![CRAN status](https://www.r-pkg.org/badges/version/paletteer)](https://cran.r-project.org/package=paletteer)
[![CRAN_Download_Badge](http://cranlogs.r-pkg.org/badges/scico)](https://CRAN.R-project.org/package=scico)
-->

The goal of paletteer is to be a comprehensize collection of color palettes in r using a common API.

## Installation

<!---
You can install the released version of paletteer from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("paletteer")
```
-->

If you want the development version then install directly from GitHub:

```{r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("EmilHvitfeldt/paletteer")
```

## Palettes

The palettes are divided into 2 groups; *discrete* and *continuous*. For discrete palette you have the choice between the *fixed width palettes* and *dynamic palettes*. Most common of the two are the fixed width palettes which have a set amout of colors which doesn't change when the number of colors requisted vary.

```{r}
library(paletteer)
pals::pal.bands(
  paletteer_d("nord", "frost"),
  paletteer_d("dutchmasters", "milkmaid"),
  paletteer_d("LaCroixColoR", "Lime"), 
  main = "Fixed width palettes",
  labels = c("nord\n frost", "dutchmasters\n milkmaid", "LaCroixColoR\n Lime")
  )
```

on the other hand we have the dynamic palettes where the colors of the palette depend on the number of colors you need.

```{r}
pals::pal.bands(
  paletteer_dynamic("cartography", "green.pal", 2),
  paletteer_dynamic("cartography", "green.pal", 5),
  paletteer_dynamic("cartography", "green.pal", 8),
  main = "Dynamic palettes",
  labels = c("cartography\n green.pal\n n = 2",
             "cartography\n green.pal\n n = 5",
             "cartography\n green.pal\n n = 6")
  )
```

Names of current avaliable dicrete palettes.

```{r}
palettes_discrete_names
```

Names of current avaliable dynamic palettes.

```{r}
palettes_dynamic_names
```

